\renewcommand*{\bibname}{References}
\bibliographystyle{plain}
\bibliography{references}

\begin{thebibliography}{18}

%========================
% Original Paper Research
%========================

\bibitem{original_paper} Tromer, et al: RSA Key Extraction via Low-Bandwidth Acoustic Cryptanalysis. Tel Aviv 2014 
\url{http://cs.tau.ac.il/~tromer/acoustic/}


%===================================
% Background: Acoustic cryptanalysis
%===================================

\bibitem{keystrokes} Researchers recover typed text using audio recording of keystrokes. Date visited: 9.oct 2014, 
\url{http://www.berkeley.edu/news/media/releases/2005/09/14_key.shtml}

\bibitem{KybdEmanation} Dmitri Asonov and Rakesh Agrawal. Keyboard Acoustic Emanations. San Jose 2004
\url{http://www.davidsalomon.name/CompSec/auxiliary/KybdEmanation.pdf}

%===========================
% Background: Data remanence
%===========================

\bibitem{data_remanence_flash} Sergei Skorobogatov. Data Remanence in Flash Memory Devices. United Kingdom 2005. 
\url{https://www.cl.cam.ac.uk/~sps32/DataRem_CHES2005.pdf}

%========================================
% Background: Differential fault analysis
%========================================

\bibitem{dfa_guo} Guo, et al. Invariance-based concurrent error detection for advanced encryption standard. New York 2012.
\url{http://dl.acm.org/citation.cfm?id=2228463}

\bibitem{dfa_aes} Giraud (2003): DFA on AES
\url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.12.1030}

%====================================
% Background: Electromagnetic attacks
%====================================

\bibitem{tempest_sans} SANS Institue. An Introduction to TEMPEST
\url{http://www.sans.org/reading-room/whitepapers/privacy/introduction-tempest-981}


%===========================
% Background: Power analysis
%===========================

\bibitem{dpa_kocher} Paul Kocher. Differential power analysis. San Francisco 1999.
\url{http://www.cryptography.com/public/pdf/DPA.pdf}

%===========================
% Background: Timing attacks
%===========================

\bibitem{ssl_timing_attack} D. Boneh and D. Brumley. Remote timing attacks are practical
\url{http://crypto.stanford.edu/~dabo/abstracts/ssl-timing.html}

\bibitem{timing_attack_kocher} Paul Kocher. Timing attacks on implementations of Diffie-Hellman, RSA, DSS and other systems. San Francisco 1996.
\url{http://www.cryptography.com/public/pdf/TimingAttacks.pdf}

%=============================================
% Knowles Ultrasonic SPU0410LR5H Configuration
%=============================================

\bibitem{knowles_spec} Knowles Ultrasonic SPU0410LR5H specification
\url{http://www.knowles.com/eng/content/download/4015/50958/version/4/file/SPU0410LR5H.pdf}

\bibitem{NI_myDAQ} National Instruments myDAQ specification
\url{http://www.ni.com/pdf/manuals/373061f.pdf}

\bibitem{NI_myDAQ_userguide} National Instruments myDAQ User Guide
\url{http://www.ni.com/pdf/manuals/373060f.pdf}

\bibitem{TI_opa1642} Texas Instruments OPA1642
\url{http://www.ti.com.cn/cn/lit/ds/symlink/opa1642.pdf}

%=============================================
% Brüel&Kjær 4191 Configuration
%=============================================

\bibitem{bk4191_spec} Brüel\&Kjær 4191 specification
\url{http://www.bksv.com/products/transducers/acoustic/microphones/microphone-cartridges/4191}

%==========
% Chapter 3
%==========

\bibitem{GnuPG_1.4.15} GnuPG 1.4.15 tar file
\url{ftp://ftp.gnupg.org/gcrypt/gnupg/gnupg-1.4.15.tar.bz2}


%==========
% Chapter 4
%==========

\bibitem{Perf_Wiki} Perf Wiki
\url{https://perf.wiki.kernel.org/index.php/Main_Page}


%======
% Other
%======

\bibitem{MIL_HDBK_232} Department of Defence, US. Red/Black Engineering-Installation Guidelines. Washington DC, 1988. Validated oct 2000 and aug 2014.
\url{https://www.wbdg.org/ccb/FEDMIL/hdbk232a.pdf}

\bibitem{NSM_avlytting} Norges Sikkerhetsmyndigheter. Sikring mot avlytting (Protection against eavesdropping). Sept 2011. 
\url{https://www.nsm.stat.no/globalassets/dokumenter/veiledninger/veiledning-i-sikring-mot-avlytting.pdf}

\end{thebibliography}